Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
DX

Model-based diagnosis is a well-known approach that has been proposed by the
DX community\Mar{I don't know what is DX. suggest to expand the
  acronym and/or cite.}\Mar{say shortly (in general terms) what is the
  goal. what is that good for.}, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.

@@

Prior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques. \Rui{not related work. more of motivation (avoid words such as believe)-->}
Although, \ds{} does not ensure the improvement of \sfl{} since it
can remove faulty statements from the failing test, we believe it has a great
potential to help reducing test cases and improve \sfl{} accuracy. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.

>>>>

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI that develops algorithms and techniques to
determine the root-cause of observed failures.~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.

@@

coPrior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques. \Rui{not related work. more of motivation (avoid words such as believe)-->}
Although, \ds{} does not ensure the improvement of \sfl{} since it
can remove faulty statements from the failing test, we believe it has a great
potential to help reducing test cases and improve \sfl{} accuracy. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.
